Binning Strategies and Related Loss for Graphics of Large Data

### 2013-03-06 Paper.Rnw
Fix extra 2 in the LossFunction() call.

LossTable <- NULL
bins <- rbind(c(2,2), c(5,25))
computeLoss <- function(binning, data){
  lRandom <- lossCalc(data, binning=binning, type="random", newData = TRUE)
  lMean <- lossCalc(data, binning=binning, type="standard", newData=TRUE)
  datplot <- rbind(cbind(lRandom$NewData, Algorithm="Random"), cbind(lMean$NewData, Algorithm="Standard"))
  qplot(G, SO, fill = Freq, geom="tile", data = datplot, 
      main=paste("Baseball: Binning by (", binning[1], ", ", binning[2],")", sep="")) + 
    facet_grid(.~Algorithm) +
    scale_fill_gradient(low="#56B1F7", high="#132B43", guide="legend", trans="log", 
                        breaks=c(1, 5, 50, 500, 5000)) + 
    theme_bw() + theme(legend.position="bottom")
  ggsave(paste("./figure/RandomStd", binning[1], binning[2], ".pdf", sep=""), 
         width=8, height=5, units="in", dpi=1200)

@@

LossTable <- do.call("rbind", lapply(1:nrow(bins), function(i) computeLoss(bins[i,], d1)))
LossTable <- as.data.frame(LossTable)
names(LossTable2) <- c("binX", "binY", "Function", "G", "SO", "Freq")
tab <- xtable(LossTable[order(LossTable[,3], LossTable[,1]),], digits=c(0, 0, 0, 0, 8, 8, 8))
@

>>>>

LossTable <- NULL
bins <- rbind(c(2,2), c(5,25))
computeLoss <- function(binning, data){
  lRandom <- lossCalc(data, binning=binning, type="random", newData=TRUE)
  lMean <- lossCalc(data, binning=binning, type="standard", newData=TRUE)
  datplot <- rbind(cbind(lRandom$NewData, Algorithm="Random"), cbind(lMean$NewData, Algorithm="Standard"))
  qplot(G, SO, fill = Freq, geom="tile", data = datplot, 
      main=paste("Baseball: Binning by (", binning[1], ", ", binning[2],")", sep="")) + 
    facet_grid(.~Algorithm) +
    scale_fill_gradient(low="#56B1F7", high="#132B43", guide="legend", trans="log", 
                        breaks=c(1, 5, 50, 500, 5000)) + 
    theme_bw() + theme(legend.position="bottom")
  ggsave(paste("./figure/RandomStd", binning[1], binning[2], ".pdf", sep=""), 
         width=8, height=5, units="in", dpi=1200)

@@

LossTable <- do.call("rbind", lapply(1:nrow(bins), function(i) computeLoss(bins[i,], d1)))
LossTable <- as.data.frame(LossTable)
names(LossTable) <- c("binX", "binY", "Function", "G", "SO", "Freq")
tab <- xtable(LossTable[order(LossTable[,3], LossTable[,1]),], digits=c(0, 0, 0, 0, 8, 8, 8))
@
